Cost-Benefit Analysis

### 2023-05-29 workflow/notebooks/cost-benefit-analysis.Rmd
Plan to plot decision curve for one model seed initially
then add ribbons for 95% CI?

- use values from confusion matrix for one representative model on a test set. or get average precision?
  - Number needed to screen (NNS) - the number of alerted patients the models must flag to identify 1 true positive. 
  - Number needed to treat (NNT) - the number of true positive patients one must treat for 1 patient to benefit from the treatment.
  - Number needed to benefit (NNB = NNS x NNT) - how many patients must be screened for 1 patient to benefit.
- assumptions
  - cost of a non-severe case
  - cost of a severe case
    - days in icu, colectomy
  - cost of possible treatments:
    - abx: metronizadole, vancomycin, fidaxomycin
    - fmt, bezlotoxumab (monoclonal antibodies)

@@

[number needed to benefit](https://academic.oup.com/jamia/article-abstract/26/12/1655/5516459)

@@

@@

>>>>

- use values from confusion matrix for one representative model on a test set. or get average precision? choose a particular sensitivity level and see the range in precision?
  - Number needed to screen (NNS) - the number of alerted patients the models must flag to identify 1 true positive. 
  - Number needed to treat (NNT) - the number of true positive patients one must treat for 1 patient to benefit from the treatment.
  - Number needed to benefit (NNB = NNS x NNT) - how many patients must be screened for 1 patient to benefit.
- assumptions
  - cost of a non-severe case
  - cost of a severe case
    - days in icu, colectomy
  - cost of possible treatments:
    - abx: metronizadole, vancomycin, fidaxomycin
    - fmt, bezlotoxumab (monoclonal antibodies)

@@

### [number needed to benefit](https://academic.oup.com/jamia/article-abstract/26/12/1655/5516459)

@@

### [decision curve analysis](https://journals.sagepub.com/doi/10.1177/0272989X06295361)

QALYs are prone to systemic biases. 
We can sidestep using them by doing decision curve analysis instead.
Weight the relative harms of FP and FN results.

- incidence of severe CDI
- net benefit = $\frac{TP}{n} - \frac{FP}{n} \times \frac{p_t}{1-p_t}$ (Peirce 1884)
- plot net benefit vs probability threshold ($p_t$).
- harm of treating with fidaxomicin instead of vancomycin: more expensive. by how much?
- assume all patients severe vs no patients severe.

```{r decision-curve}
library(here)
library(tidyverse)
perf_dat <- read_csv(here('results','performance_results_aggregated.csv'))
med_auc <- perf_dat %>% filter(dataset == 'full', outcome == 'allcause') %>% 
  summarize(med_auc = median(AUC)) %>% pull(med_auc)
med_seed <- perf_dat %>% filter(dataset == 'full', outcome == 'allcause') %>% 
  mutate(rel_diff_auc = abs(AUC - med_auc)) %>% 
  slice_min(rel_diff_auc) %>% 
  pull(seed) %>% 
  .[1]
sensspec_dat <- read_csv(here('results','sensspec_results_aggregated.csv'))
dat_med <- sensspec_dat %>% filter(dataset == 'full', outcome == 'allcause', seed == med_seed) 
sensspec_dat %>% 
  filter(dataset == 'full', outcome == 'pragmatic', precision < 0.04)
```

```{r sensspec}
model <- read_rds(here('results/predict_allcause/taxlevel_OTU/metric_AUC/dataset_full/trainfrac_0.8/runs/rf_142_model.Rds'))
test_dat <- read_csv(here('results/predict_allcause/taxlevel_OTU/metric_AUC/dataset_full/trainfrac_0.8/runs/rf_142_test-data.csv'))
preds <- stats::predict(model, test_dat, type = 'prob') %>% 
  mutate(pred_pos = yes > 0.5)
```

```{r decision-thresholds}
thresh_dat <- read_csv(here('results','thresholds_results_aggregated.csv'))
thresh_dat %>% 
  filter(dataset == 'full', outcome == 'attrib', seed == 100) %>% 
  ggplot(aes(decision_threshold, net_benefit, 
             color = strategy, linetype = strategy)) +
  geom_line(alpha = 0.6) +
  theme_sovacool()
```

@@

NNT for Fidaxomicin, FMT, and/or Bezlotoxumab. Current standard is Vancomycin
because it's cheaper than Fidaxomicin, even though IDSA recommends Fidaxomicin.

rough estimate of costs.
current: everyone gets vancomycin.
potential: patients flagged as severe get fidaxomicin. based on NNB, estimate
how much money saved in averting severe outcomes.
